State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-01-18 draft.tex
Nothing
what happened

[ticket: X]

\todo{Since we require guarantees of stability and feasibility in presence of disturbances arbitrary state constraints

@@

ones are used.}

@@

To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$. Then there exists a value of $\lambda\in(0,1)$ such that
\begin{align*}
  \{ \lambda z_1 + (1-&\lambda)z_2
  \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
  % \not\subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
  % \right\}\oplus \lambda \mathcal W(z_1) \oplus (1-\lambda)
  % \mathcal W(z_2)\\
 \not\subseteq &\lambda\bigl(\{z_1\}\oplus \mathcal W(z_1)\bigr)\oplus
  (1-\lambda)\bigl(\{z_2\}\oplus \mathcal W(z_2)\bigr) .
\end{align*}
Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
%
\textcolor{red}{I'm not sure this works. This only shows that it is necessary for polytopic sets, but polytopic sets are a subset of all possible sets. There might be sets for which this still works}
\end{proof}
%
Theorem~\ref{thm:convexity:of:pontryagin:difference} provides necessary and sufficient conditions for convexity of the parametric Pontryagin difference. In the next section we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polytopic parametric set is itself polyhedral.
%
%
%
%
%
%
\subsection{Maximal Robust Positively Invariant Sets}\label{ssec:MRPI:sets}
%
This section describes an iterative algorithm to compute the MRPI set for a linear system subject to unknown disturbances:
\[
x^+=\Psi x + v, \quad v\in\mathcal V(x),
\]
where $\mathcal V(x)$ is a continuous point-to-set map and the state $x$ is subject to the constraint $x\in\mathcal{X}$. 
%
To compute the MRPI set $\mathcal X^\infty$ we start from the constraint set $\mathcal X$ and  iteratively remove points that do not satisfy the definition~\eqref{eq:definition:MRPI:set}
by introducing constraints that exclude states for which a successor state can lie outside 
$\mathcal X$. 
%
Specifically, at each iteration $k=0,1,\ldots$, we define $\mathcal{X}_k$ as the set of initial states of the system $x^+=\Psi x + v$ such that the $i$ steps ahead state lies in $\mathcal{X}$ for all $i\in\mathbb{N}_{[0,k]}$, for all admissible disturbances. 
%
The MRPI set is then obtained as the limit of the sequence $\mathcal{X}_0,\mathcal{X}_1,\ldots$ (see e.g.~\cite{blanchini:2007}).

>>>>

Since we require guarantees of stability and feasibility in presence of disturbances arbitrary state constraints

@@

ones are used.

@@

To demonstrate that parametric convexity of $\mathcal W$ is necessary for convexity of $S\ominus \mathcal W(S)$, suppose that condition~(\ref{eq:def:parametrically:convex}) does not hold and choose $z_1,z_2$ so that $\mathcal W(\lambda z_1 + (1-\lambda) z_2) \not\subseteq \lambda \mathcal W(z_1) \oplus (1-\lambda) \mathcal W (z_2)$ for some $\lambda \in (0,1)$. Then there exists a value of $\lambda\in(0,1)$ such that
\begin{align*}
  \{ \lambda z_1 + (1-&\lambda)z_2
  \}\oplus \mathcal W\left( \lambda z_1 + (1-\lambda)z_2\right)\\
  % \not\subseteq&\left\{ \lambda z_1 + (1-\lambda)z_2
  % \right\}\oplus \lambda \mathcal W(z_1) \oplus (1-\lambda)
  % \mathcal W(z_2)\\
 \not\subseteq &\lambda\bigl(\{z_1\}\oplus \mathcal W(z_1)\bigr)\oplus
  (1-\lambda)\bigl(\{z_2\}\oplus \mathcal W(z_2)\bigr) .
\end{align*}
Therefore if $S$ is a convex polyhedron constructed so that $\{z_1\}\oplus\mathcal W(z_1)$ and $\{z_2\}\oplus\mathcal W(z_2)$ contain points lying on the same facet of $S$ (this is always possible if $S^\prime=S\ominus \mathcal W(S)$ has a non-empty interior), then there exists $\lambda \in (0,1)$ such that $\lambda z_1 + (1-\lambda) z_2 \notin S^\prime$.
%
\end{proof}
%
Theorem~\ref{thm:convexity:of:pontryagin:difference} provides necessary and sufficient conditions for convexity of the parametric Pontryagin difference. In the next section we will show that the parametric Pontryagin difference between a polyhedral set and a piecewise affine polytopic parametric set is itself polyhedral.
%
%
%
%
%
%
\subsection{Maximal Robust Positively Invariant Sets}\label{ssec:MRPI:sets}
%
This section describes an iterative algorithm to compute the MRPI set for a linear system subject to unknown disturbances:
\[
x^+=\Psi x + v, \quad v\in\mathcal V(x),
\]
where $\mathcal V(x)$ is a continuous point-to-set map and the state $x$ is subject to the constraint $x\in\mathcal{X}$. 
%
To compute the MRPI set $\mathcal X^\infty$ we start from the constraint set $\mathcal X$ and  iteratively remove points that do not satisfy the definition~\eqref{eq:definition:MRPI:set}
by introducing constraints that exclude states for which a successor state can lie outside 
$\mathcal X$. 
%
Specifically, at each iteration $k=0,1,\ldots$, we define $\mathcal{X}_k$ as the set of initial states of the system $x^+=\Psi x + v$ such that the $i$ steps ahead state lies in $\mathcal{X}$ for all $i\in\mathbb{N}_{[0,k]}$, for all admissible disturbances. 
%
The MRPI set is then obtained as the limit of the sequence $\mathcal{X}_0,\mathcal{X}_1,\ldots$ (see e.g.~\cite{blanchini:2007}).
